\documentclass[addpoints]{exam}
% leqno 將方程式編號放在左側

%\printanswers

\usepackage[top=2.5cm,bottom=2cm,left=2.5cm,right=2.5cm,headsep=10pt,a4paper]{geometry} % 引用頁面幾何套件，設定頁面邊界

\usepackage{siunitx} % 角度
% \input{NewCommands}

\usepackage{amsmath,amssymb,amsthm} % 引用常見的數學符號與設定


\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem*{theorem}{Theorem}
\newtheorem*{remark}{Remark}
\newcommand{\R}{\mathbb{R}}

\usepackage{lastpage} % 取得最後頁碼




\usepackage{graphicx} % 引用圖檔內嵌入套件
\graphicspath{{Pictures/}} % 設定圖檔目錄
\usepackage{xcolor} %引用顏色套件
\usepackage{enumerate}
\usepackage{float}
\usepackage{hyperref}
\usepackage{mdwlist} % use suspend & resume to successive enumerate

\usepackage{CJKutf8} % 設定中文

\def \lflr{\left\lfloor} %自定義 floor function
\def \rflr{\right\rfloor} %自定義

% question separation
\renewcommand{\questionshook}{%
  \setlength{\itemsep}{0.5cm}%
}

\allowdisplaybreaks %equation allowed to next page

\firstpageheader{\today}
                {}
                {}
\footer{}{\sf Page \thepage~of~\pageref{LastPage}}{}

\begin{document}

\begin{CJK*}{UTF8}{gbsn}
% Title
\begin{center}
    {\Large{\bf Introduction to Mathematical Analysis II\\
    Homework 3  Due  March 20  (Friday), 2026\\
    Please submit your group homework online in PDF format.\\
You are expected to work collaboratively within your group. 
Please do not obtain complete solutions directly from AI tools. 
The purpose of this assignment is to develop your own mathematical reasoning and problem-solving skills. %  Homework X Brief Solution
  }} \\ 
    \large
    %\text{Due date: 3/9/2023}
\end{center}

\noindent\rule{16.2cm}{0.4pt}


\begin{questions}


% ============ Question x ============
\question  (20 pts)  
\textbf{Exercise 6.6.8.}
Let $(X,d)$ be a complete metric space, and let $f:X\to X$ and $g:X\to X$ be two strict
contractions on $X$ with contraction coefficients $c$ and $c'$, respectively.
From Theorem 6.6.4 we know that $f$ has some fixed point $x_0$, and $g$ has some fixed point
$y_0$. Suppose we know that there is an $\varepsilon>0$ such that
$$
d(f(x),g(x))\le \varepsilon
\qquad \text{for all } x\in X
$$
(i.e.\ $f$ and $g$ are within $\varepsilon$ of each other in the uniform metric).
Show that
$$
d(x_0,y_0)\le \frac{\varepsilon}{1-\min(c,c')}.
$$
Thus nearby contractions have nearby fixed points.

\begin{solution} 
\begin{enumerate}
\item[(a)] 



\bigskip
\item[(b)] 


\bigskip
\item[(c)] 

\end{enumerate}

 \end{solution}

\question (20 pts) 
Let \(f:S\to S\) be a function from a metric space \((S,d)\) into itself such that
\[
d\bigl(f(x),f(y)\bigr)<d(x,y)
\]
whenever \(x\ne y\).

\begin{itemize}
\item[(a)] Prove that \(f\) has at most one fixed point, and give an example of such an \(f\) with no fixed point.
\item[(b)] If \(S\) is compact, prove that \(f\) has exactly one fixed point. \emph{Hint.} Show that
\[
g(x)=d(x,f(x))
\]
attains its minimum on \(S\).
\item[(c)] Give an example with \(S\) compact in which \(f\) is not a contraction.
\end{itemize}


\begin{solution}

\begin{enumerate}
\item[(a)] 



\bigskip
\item[(b)] 




\end{enumerate} 
\end{solution}

\question (20 pts) Let \(f:S\to S\) be a function from a complete metric space \((S,d)\) into itself. Assume there is a real sequence \(\{\alpha_n\}\) which converges to \(0\) such that
\[
d\bigl(f^n(x),f^n(y)\bigr)\le \alpha_n d(x,y)
\]
for all \(n\ge 1\) and all \(x,y\) in \(S\), where \(f^n\) is the \(n\)th iterate of \(f\); that is,
\[
f^1(x)=f(x),\qquad f^{n+1}(x)=f(f^n(x)) \qquad \text{for } n\ge 1.
\]
Prove that \(f\) has a unique fixed point. \emph{Hint.} Apply the fixed-point theorem to \(f^m\) for a suitable \(m\).


\begin{solution} 
 
 \end{solution}

\question (20 pts) \textbf{Exercise 6.7.3.}
Let $f:\mathbf{R}^n\to\mathbf{R}^n$ be a continuously differentiable function such that
$f'(x)$ is an invertible linear transformation for every $x\in\mathbf{R}^n$.
Show that whenever $V$ is an open set in $\mathbf{R}^n$, the set $f(V)$ is also open.
(\emph{Hint:} use the inverse function theorem.)


\begin{solution} 

\end{solution}

\question (20 pts) Let \(f:U\subset \mathbf{R}^n\to \mathbf{R}^n\) satisfy the hypotheses of Theorem~6.7.2, and let
$$
A:=f'(x_0).
$$
Throughout this problem, for a linear map \(T:\mathbf{R}^n\to \mathbf{R}^n\), define the Frobenius norm by
$$
\|T\|:=\sqrt{\sum_{i,j=1}^n t_{ij}^2}.
$$

This problem develops a quantitative version of the local invertibility statement in the inverse function theorem.

\begin{itemize}
\item[(a)] Show that there exists \(r>0\) such that for all \(x\in B(x_0,r)\),
$$
\|f'(x)-A\|\le \frac{1}{2\|A^{-1}\|}.
$$
(\emph{Hint:} use continuity of \(f'\) at \(x_0\).)

\item[(b)] Prove that for all \(x,y\in B(x_0,r)\),
$$
\|f(x)-f(y)-A(x-y)\|
\le
\frac{1}{2\|A^{-1}\|}\,\|x-y\|.
$$
(\emph{Hint:} consider the function \(g(z):=f(z)-Az\), and estimate \(g(x)-g(y)\) along the line segment joining \(x\) and \(y\).)

\item[(c)] Deduce that for all \(x,y\in B(x_0,r)\),
$$
\frac{1}{2\|A^{-1}\|}\,\|x-y\|
\;\le\;
\|f(x)-f(y)\|
\;\le\;
\left(\|A\|+\frac{1}{2\|A^{-1}\|}\right)\|x-y\|.
$$

\item[(d)] Conclude that the restriction of \(f\) to \(B(x_0,r)\) is one-to-one, and hence that the local inverse
$$
f^{-1}:f(B(x_0,r))\to B(x_0,r)
$$
is Lipschitz, with
$$
\|f^{-1}(u)-f^{-1}(v)\|
\le
2\|A^{-1}\|\,\|u-v\|
\qquad
\text{for all }u,v\in f(B(x_0,r)).
$$

\item[(e)] Explain briefly how the estimate in part (d) strengthens the usual qualitative conclusion of the inverse function theorem.
\end{itemize}
\begin{solution} 

\end{solution}


\end{questions}

You can do the following problems to practice. You don't have to submit the following problems.

\begin{questions}

\question   Let  \(K\subseteq \mathbf{R}^n \) be a compact subset. Consider a function \(f:K\to K\) satisfying
\[
\forall x,y\in K,\qquad \|f(x)-f(y)\|\ge \|x-y\|.
\]

Fix \(a_0,b_0\in K\), and define two iterative sequences as follows
\[
\forall n\ge 0,\qquad a_{n+1}=f(a_n)\qquad\text{and}\qquad b_{n+1}=f(b_n).
\]

\begin{itemize}
\item[(1)] Show that for all \(\varepsilon>0\) and every integer \(p\ge 1\), there exists \(k\ge p\) such that
\[
\|a_k-a_0\|<\varepsilon
\qquad\text{and}\qquad
\|b_k-b_0\|<\varepsilon.
\]

\item[(2)] Deduce  that \(f(K)\) is dense in \(K\).

\item[(3)] Consider
\[
u_n=\|a_n-b_n|\qquad\text{for }n\ge 0.
\]
Show that \((u_n)_{n\ge 0}\) is eventually constant.

\item[(4)] Deduce that \(f\) is an isometry (i.e. $d(f(x),f(y))=d(x,y)$), so injective.

\item[(5)] Show that \(f\) is surjective.
\end{itemize}

\begin{solution}

\end{solution}

\question Let $f:\mathbf{R}^2\to\mathbf{R}^2$ be defined by
\[
f(x,y):=
\begin{cases}
(x,\; y + x^2\sin(1/x^2)), & x\neq 0,\\
(x,\; y), & x=0.
\end{cases}
\]
\begin{itemize}
\item[(a)] Show that $f$ is differentiable everywhere, and compute $Df(0,0)$.
\item[(b)] Show that $Df(0,0)$ is invertible.
\item[(c)] Show that $f$ is not one-to-one on \emph{any} neighborhood of $(0,0)$.
(\emph{Hint:} for $x\neq 0$, the map translates vertical lines $x=\text{const}$ by an amount depending on $x$; produce two distinct points $(x,y_1)$ and $(x,y_2)$ that are mapped to the same image for $x$ arbitrarily small.)
\item[(d)] Conclude that the hypothesis ``$f$ is continuously differentiable'' in Theorem~6.7.2 cannot be weakened to mere differentiability.
\end{itemize}

\question
Define $f:\mathbf{R}^2\to\mathbf{R}^2$ by
\[
f(x,y):=\bigl(e^x\cos y,\; e^x\sin y\bigr).
\]
\begin{itemize}
\item[(a)] Compute the Jacobian matrix $Df(x,y)$ and show that $Df(x_0,y_0)$ is invertible for every $(x_0,y_0)\in\mathbf{R}^2$.
\item[(b)] Let $(u_0,v_0)=f(x_0,y_0)$.  Use Theorem~6.7.2 to conclude that $f$ is locally invertible near $(x_0,y_0)$.
Describe explicitly an open neighborhood $V$ of $(u_0,v_0)$ on which a local inverse can be written using polar coordinates.
\item[(c)] Compute $(f^{-1})'(u_0,v_0)$ by the formula
\[
(f^{-1})'(f(x_0,y_0))=(f'(x_0,y_0))^{-1},
\]
and verify your answer by differentiating your explicit inverse from part (b).
\end{itemize}


\end{questions}
\end{CJK*}
\end{document}

\question   

\begin{solution}

\end{solution}

\question 



\begin{solution}

\end{solution}

\question
\begin{solution}

\end{solution}





%
% \appendix
% \section{}


\question

\begin{exercise}[3.15]
Let \((V,\|\cdot\|)\) be a normed vector space and \(K\subseteq V\) be a compact subset. Consider a function \(f:K\to K\) satisfying
\[
\forall x,y\in K,\qquad \|f(x)-f(y)\|\ge \|x-y\|.
\]

Fix \(a_0,b_0\in K\), and define two iterative sequences as follows
\[
\forall n\ge 0,\qquad a_{n+1}=f(a_n)\qquad\text{and}\qquad b_{n+1}=f(b_n).
\]

\begin{itemize}
\item[(1)] Show that for all \(\varepsilon>0\) and every integer \(p\ge 1\), there exists \(k\ge p\) such that
\[
\|a_k-a_0\|<\varepsilon
\qquad\text{and}\qquad
\|b_k-b_0\|<\varepsilon.
\]

\item[(2)] Deduce from the previous question that \(f(K)\) is dense in \(K\).

\item[(3)] Consider
\[
u_n=\|a_n-b_n|\qquad\text{for }n\ge 0.
\]
Show that \((u_n)_{n\ge 0}\) is eventually constant.

\item[(4)] Deduce that \(f\) is an isometry, so injective.

\item[(5)] Show that \(f\) is surjective.
\end{itemize}
\end{exercise}



\begin{solution}

\end{solution}
